Automated topic naming to support analysis of software maintenance activities

### 2010-08-16 icse/icse2011.tex
updates for timeline view

\subsection{Generating the data}
\label{sec:wordlist}
To evaluate our approach, we sought candidate systems that were mature projects and had openly accessible source control repositories. We selected systems from the same application domain, so the functional requirements would be broadly similar. We selected MySQL and MaxDB as they were open-source, partially-commercial database systems. MaxDB started in the late 1970s as a research project, and was later acquired by SAP. As of version 7.500, released April 2007, the project has 940 thousand lines of C source code~\footnote{generated using David A. Wheeler's \emph{SLOCCount}.}. The MySQL project started in 1994 and MySQL 3.23 was released in early 2001. MySQL contains 320 thousand lines of C and C++ source code. 
\todo[inline]{why 3.23 and not newer?}

@@

\begin{figure*}%[h]
  \centering
  % hi-res version
  %\includegraphics[width=.97\textwidth]{mysql-time-smear-plot-Equal}
  \includegraphics[width=.97\textwidth]{small-mysql-time-smear-plot-Equal}
  %\includegraphics[width=.97\textwidth]{small-mysql-time-smear-plot-Equal}
  \caption{MySQL 3.23: Labelled topics related to non-functional software qualities plotted over time, continuous topics are trends that occur across time}
  \label{fig:mysql}
\end{figure*}

>>>>

\subsection{Generating the data}
\label{sec:wordlist}
To evaluate our approach, we sought candidate systems that were mature projects and had openly accessible source control repositories. We selected systems from the same application domain, so the functional requirements would be broadly similar. We selected MySQL and MaxDB as they were open-source, partially-commercial database systems. MaxDB started in the late 1970s as a research project, and was later acquired by SAP. As of version 7.500, released April 2007, the project has 940 thousand lines of C source code~\footnote{generated using David A. Wheeler's \emph{SLOCCount}.}. The MySQL project started in 1994 and MySQL 3.23 was released in early 2001. MySQL contains 320 thousand lines of C and C++ source code.  Choosing an older version of these projects allows us to focus on projects which have moved into the maintenance phase of the software lifecycle.

@@

\begin{figure*}%[h]
  \centering
  % hi-res version
  %\includegraphics[width=.97\textwidth]{mysql-time-smear-plot-Equal}
  %\includegraphics[width=.97\textwidth]{small-mysql-time-smear-plot-Equal}
  \includegraphics[width=.97\textwidth]{mysql-timeline}
  \caption{MySQL 3.23:NFRs over time. Topic frequency is mapped to alpha (transparency) value.}
  \label{fig:mysql}
\end{figure*}
